KidsAIR: merge exposure datasets

### 2020-04-01 ambient_initial.Rmd
ambient analysis updates

```{r, message=FALSE}
library(tidyverse)
library(readxl)
library(naniar)
library(lubridate)
library(broom)
library(broom.mixed)
library(zoo)
library(lme4)
library(lmerTest)
library(ggmap)
library(maps)
jv_palette <- c("#330099","#CC0066","#FF6633", 
                 "#0099CC", "#FF9900","#CC6633",
                  "#FF3366", "#33CC99", "#33999")
```

@@

us_zipcodes <- read_tsv("Input/us_zipcodes/us_zipcodes.txt", 
                        col_names = c("country", "zip", "city", "state",
                                      "state_abbr", "trash1", "trash2", "trash3", 
                                      "trash4", "lat", "long", "trash5")) %>% 
  select(-trash1:-trash4, -trash5)

@@

ak_map <- map_data("state") %>% 
  filter(region == "alaska")

us_temp_stations <- read_table("Input/ambient/temp_station_list.txt", skip = 20,
                            col_names = c("station", "wban", "station_names",
                                          "country", "state", "call", "lat",
                                          "long", "elevation", "begin_date",
                                          "end_date")) %>% 
  filter(country == "US") %>% 
  mutate(lat = as.numeric(lat),
         long = as.numeric(long),
         elevation = as.numeric(elevation),
         begin_date = ymd(begin_date),
         end_date = ymd(end_date))

pm_stations <- read_xlsx("Input/ambient/pm_station_list.xlsx")
```

# Mapping zipcodes, weather stations, pm stations - WMT
```{r}
wmt_zipcodes_new <- wmt_zipcodes %>% 
  left_join(us_zipcodes, by = "zip") %>% 
  distinct(zip, .keep_all = TRUE) %>% 
  mutate(lat_zip = lat,
         long_zip = long)

#Plot temp stations
wmt_temp_stations <- us_temp_stations %>% 
  filter(state == "MT" | state == "ID") %>% 
  mutate(lat_temp = lat,
         long_temp = long) %>% 
  filter(begin_date < "2014-06-01") %>% 
  filter(end_date > "2020-03-21") %>% 
  #distinct(station, .keep_all = TRUE) %>% 
  full_join(wmt_zipcodes_new, by = "country") %>% 
  mutate(lat_diff = abs(lat_zip - lat_temp),
         long_diff = abs(long_zip - long_temp),
         sum_diff = lat_diff + long_diff,
         area = "WMT") %>% 
  arrange(zip, sum_diff) %>% 
  distinct(zip, .keep_all = TRUE) %>% 
  filter(!is.na(home)) %>% 
  mutate(station_char = factor(station_names, 
                               levels = c("BERT MOONEY AIRPORT", "GLACIER PARK INTERNATIONAL AI",
                                          "GOLF (SIMMS)", "HELENA REGIONAL AIRPORT",
                                          "LEMHI COUNTY AIRPORT", "MISSOULA INTERNATIONAL AIRPOR",
                                          "MULLAN PASS"),
                               labels = c("bertmooneyairport", "glacierparkairport",
                                          "golfsimms", "helenaairport",
                                          "lemhicountyairport", "missoulaairport",
                                          "mullanpass"))) %>% 
  select(area, station, station_char, zip, elevation, lat_temp, long_temp, lat_zip, 
         long_zip, station_names)

wmt_plot <- wmt_zipcodes_new %>% 
  ggplot() +
    geom_polygon(data=wmt_map, aes(x=long, y=lat, group=group), 
               colour="black", fill = "white") +
    geom_point(data=wmt_temp_stations, 
             aes(long_zip, lat_zip, color = station_names), size = 3) +
    geom_point(data=wmt_temp_stations, 
             aes(long_temp, lat_temp, color = station_names), 
             shape = 15, size = 3) +
    theme_void() +
    scale_color_manual(values = jv_palette)
wmt_plot

#Plot PM stations
wmt_pm_stations <- pm_stations %>% 
  filter(area == "WMT") %>% 
  full_join(wmt_zipcodes_new, by = "country") %>% 
  mutate(lat_diff = abs(lat_zip - lat_pm),
         long_diff = abs(long_zip - long_pm),
         sum_diff = lat_diff + long_diff) %>% 
  arrange(zip, sum_diff) %>% 
  distinct(zip, .keep_all = TRUE) %>% 
  filter(!is.na(home)) %>% 
  select(area, local_site, zip, lat_pm, long_pm, lat_zip, long_zip)

wmt_plot <- wmt_zipcodes_new %>% 
  ggplot() +
    geom_polygon(data=wmt_map, aes(x=long, y=lat, group=group), 
               colour="black", fill = "white") +
    geom_point(data=wmt_pm_stations, 
             aes(long_zip, lat_zip, color = local_site), size = 3) +
    geom_point(data=wmt_pm_stations, 
             aes(long_pm, lat_pm, color = local_site), 
             shape = 15, size = 3) +
    theme_void() +
    scale_color_manual(values = jv_palette)
wmt_plot
```

@@

nn_plot_temp_stations <- wmt_zipcodes_new %>% 
  ggplot() +
    geom_polygon(data=nn_map, aes(x=long, y=lat, group=group), 
               colour="black", fill = "white") +
    geom_point(data=nn_temp_stations, 
             aes(long_zip, lat_zip, color = station_names), size = 3) +
    geom_point(data=nn_temp_stations, 
             aes(long_temp, lat_temp, color = station_names), 
             shape = 15, size = 3) +
    theme_void() +
    scale_color_manual(values = jv_palette)
nn_plot_temp_stations

@@

nn_plot <- nn_zipcodes_new %>% 
  ggplot() +
    geom_polygon(data=nn_map, aes(x=long, y=lat, group=group), 
               colour="black", fill = "white") +
    geom_point(data=nn_pm_stations, 
             aes(long_zip, lat_zip, color = local_site), size = 3) +
    geom_point(data=nn_pm_stations, 
             aes(long_pm, lat_pm, color = local_site), 
             shape = 15, size = 3) +
    theme_void() +
    scale_color_manual(values = jv_palette)
nn_plot
```

@@

zipcodes_map <- wmt_zipcodes_new %>% 
  ggplot() +
    geom_point(data=ak_temp_stations, 
             aes(long_zip, lat_zip, color = station_names), size = 3) +
    geom_point(data=ak_temp_stations, 
             aes(long_temp, lat_temp, color = station_names), 
             shape = 15, size = 3) +
    theme_void() +
    scale_color_manual(values = jv_palette) 
zipcodes_map

@@

ak_plot <- ak_zipcodes_new %>% 
  ggplot() +
    geom_polygon(data=ak_map, aes(x=long, y=lat, group=group), 
               colour="black", fill = "white") +
    geom_point(data=ak_pm_stations, 
             aes(long_zip, lat_zip, color = local_site), size = 3) +
    geom_point(data=ak_pm_stations, 
             aes(long_pm, lat_pm, color = local_site), 
             shape = 15, size = 3) +
    theme_void() +
    scale_color_manual(values = jv_palette)
ak_plot
```

# Compile temperature data and filter for closest stations
```{r}
list_files <- list.files("Input/ambient/temp_data")
# Set working directory and load files in list; extract file name and add as column
## run next 4 lines together
setwd("Input/ambient/temp_data") # set new working directory
initial_data = tibble(file_name = list_files) %>% # use list of files from above
  mutate(save_data = lapply(file_name, read_csv, 
                            col_names = c("station", "wban", "temp_date",
                                          "mean_temp", "t1", "mean_dewp", "t2",
                                          "t3", "t4", "mean_pressure", "t5",
                                          "mean_visib_miles", "t6", "mean_wind_knots",
                                          "t7", "max_wind_knots", "t8", "max_temp",
                                          "min_temp", "precip", "snow_depth", "t9"))) %>%
  unnest(save_data)

# Format combined file from above; combine with other PM data below
temp_data <- initial_data %>% 
  filter(!is.na(t1)) %>% 
  separate(file_name, c("area", "station_char"), sep = "_") %>%
  mutate(temp_date = ymd(temp_date),
         mean_temp = as.numeric(mean_temp),
         mean_dewp = as.numeric(mean_dewp),
         mean_pressure = as.numeric(mean_pressure),
         mean_visib_miles = as.numeric(mean_visib_miles),
         mean_wind_knots = as.numeric(mean_wind_knots),
         max_wind_knots = as.numeric(max_wind_knots)) %>% 
  select(station_char, station, temp_date, mean_temp, mean_dewp,
         mean_pressure, mean_visib_miles, mean_wind_knots, max_wind_knots) %>% 
  replace_with_na_all(condition = ~.x %in% c(9999.9, 999.9))

temp_stations <- rbind(wmt_temp_stations, nn_temp_stations, ak_temp_stations)

temp_data_joined <- temp_data %>% 
  left_join(temp_stations, by = c("station", "station_char"))

@@

list_files <- list.files("Input/ambient/pm_data")
# Set working directory and load files in list; extract file name and add as column
## run next 4 lines together
setwd("Input/ambient/pm_data") # set new working directory
initial_data = tibble(file_name = list_files) %>% # use list of files from above
   mutate(save_data = lapply(file_name, read_csv, skip = 1,
                            col_names = c("t1", "t2", "t3", "t4", "parameter",
                                          "pm_lat", "pm_long", "t5", "parameter_name",
                                          "duration", "pollutant", "amb_pm_date",
                                          "year", "t6", "units", "t7", "t8", "t9",
                                          "t10", "t11", "mean_pollution", "t12",
                                          "t13", "t14", "aqi", "t15", "t16",
                                          "t17", "t18", "t19", "local_site",
                                          "t20", "t21", "t22"),
                            col_types = list(col_character(), col_character(), 
                                          col_character(), col_character(), 
                                          col_character(), col_double(), 
                                          col_double(), col_character(), 
                                          col_character(), col_character(), 
                                          col_character(), col_character(), 
                                          col_character(), col_character(), 
                                          col_character(), col_character(), 
                                          col_character(), col_character(),
                                          col_character(), col_character(), 
                                          col_double(), col_character(),
                                          col_character(), col_character(), 
                                          col_character(), col_character(), 
                                          col_character(), col_character(), 
                                          col_character(), col_character(), 
                                          col_character(), col_character(), 
                                          col_character(), col_character()))) %>%
  unnest(save_data)

pm_data <- initial_data %>% 
  filter(t1 != "State Code") %>% 
  filter(pollutant == "PM25 24-hour 2012") %>% 
  select(local_site, pollutant, amb_pm_date, mean_pollution) %>% 
  mutate(amb_pm_24hr = as.numeric(mean_pollution),
         date1 = ymd(amb_pm_date),
         date2 = mdy(amb_pm_date)) %>% 
  unite(amb_pm_date, c("date1", "date2"), sep = "") %>% 
  separate(amb_pm_date, c("trash", "amb_pm_date"), sep = "NA") %>% 
  unite(amb_pm_date, c("trash", "amb_pm_date"), sep = "") %>% 
  group_by(local_site, amb_pm_date) %>% 
  distinct(pollutant, .keep_all = TRUE) %>% 
  select(local_site, amb_pm_date, amb_pm_24hr)
  arrange(local_site, amb_pm_date)

pm_stations <- rbind(wmt_pm_stations, nn_pm_stations, ak_pm_stations)

pm_data_joined <- pm_data %>% 
  left_join(pm_stations, by = "local_site")

>>>>

```{r, message=FALSE}
library(tidyverse)
library(readxl)
library(naniar)
library(lubridate)
library(broom)
library(broom.mixed)
library(zoo)
library(lme4)
library(lmerTest)
library(ggmap)
library(maps)
library(tigris)
jv_palette <- c("#330099","#CC0066","#FF6633", 
                 "#0099CC", "#FF9900","#CC6633",
                  "#FF3366", "#33CC99", "#33999")
```

@@

# Zipcode data from: http://download.geonames.org/export/dump/ 
us_zipcodes <- read_tsv("Input/us_zipcodes/us_zipcodes.txt", 
                        col_names = c("country", "zip", "city", "state",
                                      "state_abbr", "trash1", "trash2", "trash3", 
                                      "trash4", "lat", "long", "trash5")) %>% 
  select(-trash1:-trash4, -trash5)

@@

ak_map <- map_data("world") %>% 
  filter(subregion == "Alaska") %>% 
  filter(long < 0)

# Weather data and stations comes from the National Climatic Data Center:
# https://www7.ncdc.noaa.gov/CDO/cdoselect.cmd?datasetabbv=GSOD&countryabbv=&georegionabbv=
us_temp_stations <- read_table("Input/ambient/temp_station_list.txt", skip = 20,
                            col_names = c("station", "wban", "station_names",
                                          "country", "state", "call", "lat",
                                          "long", "elevation", "begin_date",
                                          "end_date")) %>% 
  filter(country == "US") %>% 
  mutate(lat = as.numeric(lat),
         long = as.numeric(long),
         elevation = as.numeric(elevation),
         begin_date = ymd(begin_date),
         end_date = ymd(end_date))

# Ambient PM data comes from EPA Air Quality Monitors:
# https://epa.maps.arcgis.com/apps/webappviewer/index.html?id=5f239fd3e72f424f98ef3d5def547eb5&extent=-146.2334,13.1913,-46.3896,56.5319 
pm_stations <- read_xlsx("Input/ambient/pm_station_list.xlsx")
```

# Mapping zipcodes, weather stations, pm stations - WMT
# These steps are repeated for NN and AK below
```{r}
# Zipcodes for each KidsAIR study home were downloaded from the server
# If there was no zipcode provided, the zipcode from the nearest town was used
# Here, WMT zipcodes are joined with the US zipcode data
# This step gives lat/long coordinates for each WMT zipcode
wmt_zipcodes_new <- wmt_zipcodes %>% 
  left_join(us_zipcodes, by = "zip") %>% 
  distinct(zip, .keep_all = TRUE) %>% 
  mutate(lat_zip = lat,
         long_zip = long)

# US weather stations list was filtered for MT and ID locations
# Stations were further filtered for data availability during study dates
# Temp data was joined with WMT zipcode data
# Lat/long differences were calculated
# The weather station closest to each zipcode was selected and plotted below
wmt_temp_stations <- us_temp_stations %>% 
  filter(state == "MT" | state == "ID") %>% 
  mutate(lat_temp = lat,
         long_temp = long) %>% 
  filter(begin_date < "2014-06-01") %>% 
  filter(end_date > "2020-03-21") %>% 
  #distinct(station, .keep_all = TRUE) %>% 
  full_join(wmt_zipcodes_new, by = "country") %>% 
  mutate(lat_diff = abs(lat_zip - lat_temp),
         long_diff = abs(long_zip - long_temp),
         sum_diff = lat_diff + long_diff,
         area = "WMT") %>% 
  arrange(zip, sum_diff) %>% 
  distinct(zip, .keep_all = TRUE) %>% 
  filter(!is.na(home)) %>% 
  mutate(station_char = factor(station_names, 
                               levels = c("BERT MOONEY AIRPORT", "GLACIER PARK INTERNATIONAL AI",
                                          "GOLF (SIMMS)", "HELENA REGIONAL AIRPORT",
                                          "LEMHI COUNTY AIRPORT", "MISSOULA INTERNATIONAL AIRPOR",
                                          "MULLAN PASS"),
                               labels = c("bertmooneyairport", "glacierparkairport",
                                          "golfsimms", "helenaairport",
                                          "lemhicountyairport", "missoulaairport",
                                          "mullanpass"))) %>% 
  select(area, station, station_char, zip, elevation, lat_temp, long_temp, lat_zip, 
         long_zip, station_names)

# Here, zipcodes and weather stations are plotted on a map
# Colors match for weather stations and zips that are closest together
wmt_plot <- wmt_zipcodes_new %>% 
  ggplot() +
    geom_polygon(data=wmt_map, aes(x=long, y=lat, group=group), 
               colour="black", fill = "white") +
    geom_point(data=wmt_temp_stations, 
             aes(long_zip, lat_zip, color = station_names), size = 3) +
    geom_point(data=wmt_temp_stations, 
             aes(long_temp, lat_temp, color = station_names), 
             shape = 15, size = 3) +
    theme_void() +
    labs(title = "WMT zipcodes and weather stations") +
    scale_color_manual(values = jv_palette)
wmt_plot

# Lat/long coordinates for PM stations was manually extracted from the EPA site
# Similar to weather stations, each WMT zipcode was matched with the closest PM monitor
wmt_pm_stations <- pm_stations %>% 
  filter(area == "WMT") %>% 
  full_join(wmt_zipcodes_new, by = "country") %>% 
  mutate(lat_diff = abs(lat_zip - lat_pm),
         long_diff = abs(long_zip - long_pm),
         sum_diff = lat_diff + long_diff) %>% 
  arrange(zip, sum_diff) %>% 
  distinct(zip, .keep_all = TRUE) %>% 
  filter(!is.na(home)) %>% 
  select(area, local_site, zip, lat_pm, long_pm, lat_zip, long_zip)

# PM monitors and zipcodes are plotted below
# Colors match for PM monitors and zips that are closest together
wmt_plot <- wmt_zipcodes_new %>% 
  ggplot() +
    geom_polygon(data=wmt_map, aes(x=long, y=lat, group=group), 
               colour="black", fill = "white") +
    geom_point(data=wmt_pm_stations, 
             aes(long_zip, lat_zip, color = local_site), size = 3) +
    geom_point(data=wmt_pm_stations, 
             aes(long_pm, lat_pm, color = local_site), 
             shape = 15, size = 3) +
    theme_void() +
    labs(title = "WMT zipcodes and PM monitors") +
    scale_color_manual(values = jv_palette)
wmt_plot
```

@@

nn_plot_temp_stations <- wmt_zipcodes_new %>% 
  ggplot() +
    geom_polygon(data=nn_map, aes(x=long, y=lat, group=group), 
               colour="black", fill = "white") +
    geom_point(data=nn_temp_stations, 
             aes(long_zip, lat_zip, color = station_names), size = 3) +
    geom_point(data=nn_temp_stations, 
             aes(long_temp, lat_temp, color = station_names), 
             shape = 15, size = 3) +
    theme_void() +
    labs(title = "NN zipcodes and weather stations") +
    scale_color_manual(values = jv_palette)
nn_plot_temp_stations

@@

nn_plot <- nn_zipcodes_new %>% 
  ggplot() +
    geom_polygon(data=nn_map, aes(x=long, y=lat, group=group), 
               colour="black", fill = "white") +
    geom_point(data=nn_pm_stations, 
             aes(long_zip, lat_zip, color = local_site), size = 3) +
    geom_point(data=nn_pm_stations, 
             aes(long_pm, lat_pm, color = local_site), 
             shape = 15, size = 3) +
    theme_void() +
    labs(title = "NN zipcodes and PM monitors") +
    scale_color_manual(values = jv_palette)
nn_plot
```

@@

zipcodes_map <- wmt_zipcodes_new %>% 
  ggplot() +
    geom_polygon(data=ak_map, aes(x=long, y=lat, group=group), 
               colour="black", fill = "white") +
    geom_point(data=ak_temp_stations, 
             aes(long_zip, lat_zip, color = station_names), size = 3) +
    geom_point(data=ak_temp_stations, 
             aes(long_temp, lat_temp, color = station_names), 
             shape = 15, size = 3) +
    theme_void() +
    labs(title = "AK zipcodes and weather stations") +
    scale_color_manual(values = jv_palette) 
zipcodes_map

@@

ak_plot <- ak_zipcodes_new %>% 
  ggplot() +
    geom_polygon(data=ak_map, aes(x=long, y=lat, group=group), 
               colour="black", fill = "white") +
    geom_point(data=ak_pm_stations, 
             aes(long_zip, lat_zip, color = local_site), size = 3) +
    geom_point(data=ak_pm_stations, 
             aes(long_pm, lat_pm, color = local_site), 
             shape = 15, size = 3) +
    theme_void() +
    labs(title = "AK zipcodes and PM monitors") +
    scale_color_manual(values = jv_palette)
ak_plot
```

# Compile temperature data and filter for closest stations
```{r}
# Read in ambient weather files and bind together
list_files <- list.files("Input/ambient/temp_data")
# Set working directory and load files in list; extract file name and add as column
## run next 10 lines together
setwd("Input/ambient/temp_data") # set new working directory
initial_data = tibble(file_name = list_files) %>% # use list of files from above
  mutate(save_data = lapply(file_name, read_csv, 
                            col_names = c("station", "wban", "temp_date",
                                          "mean_temp", "t1", "mean_dewp", "t2",
                                          "t3", "t4", "mean_pressure", "t5",
                                          "mean_visib_miles", "t6", "mean_wind_knots",
                                          "t7", "max_wind_knots", "t8", "max_temp",
                                          "min_temp", "precip", "snow_depth", "t9"))) %>%
  unnest(save_data)

# Format combined file from above
temp_data <- initial_data %>% 
  filter(!is.na(t1)) %>% 
  separate(file_name, c("area", "station_char"), sep = "_") %>%
  mutate(temp_date = ymd(temp_date),
         mean_temp = as.numeric(mean_temp),
         mean_dewp = as.numeric(mean_dewp),
         mean_pressure = as.numeric(mean_pressure),
         mean_visib_miles = as.numeric(mean_visib_miles),
         mean_wind_knots = as.numeric(mean_wind_knots),
         max_wind_knots = as.numeric(max_wind_knots)) %>% 
  select(station_char, station, temp_date, mean_temp, mean_dewp,
         mean_pressure, mean_visib_miles, mean_wind_knots, max_wind_knots) %>% 
  replace_with_na_all(condition = ~.x %in% c(9999.9, 999.9))

# Bind together weather station names from each location
temp_stations <- rbind(wmt_temp_stations, nn_temp_stations, ak_temp_stations)

# Join weather data with station names
temp_data_joined <- temp_data %>% 
  left_join(temp_stations, by = c("station", "station_char"))

@@

# Read in ambient PM files and bind together
list_files <- list.files("Input/ambient/pm_data")
# Set working directory and load files in list; extract file name and add as column
## run next 28 lines together
setwd("Input/ambient/pm_data") # set new working directory
initial_data = tibble(file_name = list_files) %>% # use list of files from above
   mutate(save_data = lapply(file_name, read_csv, skip = 1,
                            col_names = c("t1", "t2", "t3", "t4", "parameter",
                                          "pm_lat", "pm_long", "t5", "parameter_name",
                                          "duration", "pollutant", "amb_pm_date",
                                          "year", "t6", "units", "t7", "t8", "t9",
                                          "t10", "t11", "mean_pollution", "t12",
                                          "t13", "t14", "aqi", "t15", "t16",
                                          "t17", "t18", "t19", "local_site",
                                          "t20", "t21", "t22"),
                            col_types = list(col_character(), col_character(), 
                                          col_character(), col_character(), 
                                          col_character(), col_double(), 
                                          col_double(), col_character(), 
                                          col_character(), col_character(), 
                                          col_character(), col_character(), 
                                          col_character(), col_character(), 
                                          col_character(), col_character(), 
                                          col_character(), col_character(),
                                          col_character(), col_character(), 
                                          col_double(), col_character(),
                                          col_character(), col_character(), 
                                          col_character(), col_character(), 
                                          col_character(), col_character(), 
                                          col_character(), col_character(), 
                                          col_character(), col_character(), 
                                          col_character(), col_character()))) %>%
  unnest(save_data)

# Format combined file from above
pm_data <- initial_data %>% 
  filter(t1 != "State Code") %>% 
  filter(pollutant == "PM25 24-hour 2012") %>% 
  select(local_site, pollutant, amb_pm_date, mean_pollution) %>% 
  mutate(amb_pm_24hr = as.numeric(mean_pollution),
         date1 = ymd(amb_pm_date),
         date2 = mdy(amb_pm_date)) %>% 
  unite(amb_pm_date, c("date1", "date2"), sep = "") %>% 
  separate(amb_pm_date, c("trash", "amb_pm_date"), sep = "NA") %>% 
  unite(amb_pm_date, c("trash", "amb_pm_date"), sep = "") %>% 
  group_by(local_site, amb_pm_date) %>% 
  distinct(pollutant, .keep_all = TRUE) %>% 
  select(local_site, amb_pm_date, amb_pm_24hr)
  arrange(local_site, amb_pm_date)

# Bind together PM monitor names from each location
pm_stations <- rbind(wmt_pm_stations, nn_pm_stations, ak_pm_stations)

# Join PM data with monitor names
pm_data_joined <- pm_data %>% 
  left_join(pm_stations, by = "local_site")

### 2020-04-01 merge_datasets.Rmd
ambient analysis updates

# Update long dataset -- REMEMBER TO UPDATE SHORT DATA BELOW
```{r}
exposure_analysis_data_long <- read_rds("Output/exposure_analysis_data_long.rds")
kids_amb_pm_data <- read_rds("Output/kids_amb_pm_data_new.rds") %>% 
  mutate(sample_date = amb_pm_date)
kids_amb_temp_data <- read_rds("Output/kids_amb_temp_data_new.rds") %>% 
  mutate(sample_date = temp_date) %>% 
  mutate(sample_date = as.character(sample_date)) %>% 
  select(-lat_zip, -long_zip)
wmt_zipcodes <- read_csv("Input/WMT/wmt_zipcodes.csv") %>% 
  rename_all(tolower)
nn_zipcodes <- read_csv("Input/NN/nn_zipcodes.csv") %>% 
  rename_all(tolower)
ak_zipcodes <- read_csv("Input/AK/ak_zipcodes.csv") %>% 
  rename_all(tolower)
kids_zipcodes <- rbind(wmt_zipcodes, nn_zipcodes, ak_zipcodes) %>% 
  mutate(home = gsub(home, pattern = "_", replacement = ""))

@@

exposure_analysis_data_medium <- exposure_analysis_data_long_new %>% 
  select(area, home, home_winter_id, winter_id, treatment, 
         sampling_day, sample_date, burn_level:mean_temp_roll_4day) %>% 
  group_by(area, home, winter_id, child_id_char) %>% 
  distinct(sampling_day, .keep_all = TRUE) %>% 
  select(area, home, home_winter_id, winter_id, treatment, sampling_day,
         child_id_char, burn_level:mean_temp_roll_4day) %>% 
  mutate(filter_var = if_else(winter_id == 1 & is.na(sampling_day) & lead(sampling_day) == 1, 1, 0),
         filter_var = if_else(is.na(filter_var), 0, filter_var)) %>% 
  select(filter_var, area:mean_temp_roll_4day) %>% 
  filter(filter_var == 0) %>% 
  select(-filter_var)

>>>>

# Update long dataset -- REMEMBER TO UPDATE SHORT DATA BELOW
```{r}
exposure_analysis_data_long <- read_rds("Output/exposure_analysis_data_long.rds")
kids_amb_pm_data <- read_rds("Output/kids_amb_pm_data_new.rds") %>% 
  mutate(sample_date = amb_pm_date) %>% 
  distinct(zip, .keep_all = TRUE)
kids_amb_temp_data <- read_rds("Output/kids_amb_temp_data_new.rds") %>% 
  mutate(sample_date = temp_date) %>% 
  mutate(sample_date = as.character(sample_date)) %>% 
  distinct(zip, .keep_all = TRUE)
wmt_zipcodes <- read_csv("Input/WMT/wmt_zipcodes.csv") %>% 
  rename_all(tolower)
nn_zipcodes <- read_csv("Input/NN/nn_zipcodes.csv") %>% 
  rename_all(tolower) 
ak_zipcodes <- read_csv("Input/AK/ak_zipcodes.csv") %>% 
  rename_all(tolower) 
kids_zipcodes <- rbind(wmt_zipcodes, nn_zipcodes, ak_zipcodes) %>% 
  mutate(home = gsub(home, pattern = "_", replacement = ""),
         home = gsub(home, pattern = " ", replacement = "")) %>% 
  left_join(kids_amb_pm_data, by = "zip") %>% 
  select(home, zip, lat_pm, long_pm) %>% 
  left_join(kids_amb_temp_data, by = "zip") %>% 
  select(home, zip, lat_zip, long_zip, lat_pm, long_pm, lat_temp, long_temp)
kids_amb_pm_data <- read_rds("Output/kids_amb_pm_data_new.rds") %>% 
  mutate(sample_date = amb_pm_date) %>% 
  select(-lat_zip, -long_zip, -lat_pm, -long_pm)
kids_amb_temp_data <- read_rds("Output/kids_amb_temp_data_new.rds") %>% 
  mutate(sample_date = temp_date) %>% 
  mutate(sample_date = as.character(sample_date)) %>% 
  select(-lat_zip, -long_zip, -lat_temp, -long_temp)

@@

exposure_analysis_data_medium <- exposure_analysis_data_long_new %>% 
  select(area, home, home_winter_id, winter_id, treatment, 
         sampling_day, sample_date, burn_level:mean_temp_roll_4day) %>% 
  group_by(area, home, winter_id, child_id_char) %>% 
  distinct(sampling_day, .keep_all = TRUE) %>% 
  select(area, home, home_winter_id, winter_id, treatment, sampling_day,
         child_id_char, burn_level:mean_temp_roll_4day) %>% 
  mutate(filter_var = if_else(winter_id == 1 & is.na(sampling_day) & lead(sampling_day) == 1, 1, 0),
         filter_var = if_else(is.na(filter_var), 0, filter_var)) %>% 
  select(filter_var, area:mean_temp_roll_4day) %>% 
  filter(filter_var == 0) %>% 
  select(-filter_var) %>% 
  ungroup()
